The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
conclusions

Silk et al. (2018) presented some key multilayer questions in animal behaviour research. While these questions represent an importanting starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:

@@

  3)

>>>>

Silk et al. (2018) presented some key multilayer questions in animal behaviour research. While these questions represent an important starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:

@@

  3) How, and why, does the spatial scale of perception influence, e.g. auditory, visual, or chemotaxis, influence the  social environment across scales? What is the role of memory, and by extension social and spatial cognition, as animals navigate their environment and make decisions about where to move next?
